### 2019-08-20 thesis.tex
*** empty log message ***

Above, looking at the first noneigenmode term, in blue, one may notice
the extreme similarity with its previous expression, which describes the
spontaneous scattering process. In fact, this term is nothing but a
\emph{correction} to the spontaneous scattering process. Colored in
dark-green is the new, rigorous expression for the \emph{collisional
  damping}. The pink equation in the end, depicts the so-far unknown
\emph{electrostatic bremsstrahlung} process. The final expressions for
the three new contributions to the wave kinetic equation are right below.

@@

\chapter{Weakly turbulent processes in the presence of
  collisional interactions}
\label{main}
The generalization introduced in \cite{YZKS16} and summarized
in \Cref{noneigenmode}, is an innovative approach, in
which the contribution of the usually neglected noneigenmode
fluctuations is taken into account along with the well-known
eigenmodes contribution. The outcome of this new formulation
is a first principles theory that combines both collective
and non-collective processes, assuming the propagation of
electrostatic oscillations in unmagnetized plasmas, without
any \emph{ad hoc} addition. Such theory is the basis of the
present research, whose primary objective is performing
numerical analysis of the generalized weak turbulence
equations, and then investigate its applications on the
description and interpretation of space plasma phenomena.
More specifically, the solar plasma, where the results of
the first two analysis \cite{Tigik2016b,Tigik2017a} have
shown a promising perspective. In this chapter, we discuss
some important aspects regarding the work that has been
done until the moment and the employed methodology. Then,
we present the results in the form of appended papers, in
chronological order, in \Cref{coll-damp,sec:gen-supr}.

@@

The following paper is fairly self-sustained regarding the theory
and methods applied. All important equations are there, including
their normalized form and the normalization constants. Any doubt
related to the origin of the new equations are filled by
\Cref{noneigenmode}.

@@

\subsection{Dimensionless equations}
In order to simplify the numerical analysis, it is convenient to write
the equations in terms of dimensionless variables. Thus, let us start
by some important definitions
\begin{align*}
  z\equiv \frac{\omega}{\omega_{pe}},
  & \quad \tau\equiv \omega_{pe}t, \quad
    {\bf q}\equiv \frac{{\bf k}v_e}{\omega_{pe}}, \quad
    {\bf u}\equiv \frac{\bf v}{v_e},\\
  \mu_{\bf q}^L
  = 1,&\quad\mu_{\bf q}^S = \frac{q^3}{2^{3/2}}
	\,\sqrt{\frac{m_e}{m_i}}\;\biggl(1+\frac{3T_i}{T_e}\biggr)^{1/2},
\end{align*}
\begin{align*}
  \Phi_a({\bf u})=  v_e^3 F_a({\bf u}),& \quad
    \calE_{\bf q}^{\sigma\alpha}= \frac{(2\pi)^2 g}{m_ev_e^2}
    \frac{I_{\bf k}^{\sigma\alpha}}{\mu_{\bf k}^\alpha},\quad
    P_{\bf k}^\alpha=\frac{m_ev_e^2}{(2\pi)^2g}\omega_{pe}P_{\bf q}^\alpha,\\
\end{align*}
where $g=1/[2^{3/2}\,(4\pi)^2\,\hat{n}\,\lambda_{De}^3]$ is the
plasma parameter, $\lambda_{De}=T_e/(4\pi\hat{n}e^2)=v_e^2/(2\omega_{pe}^2)$,
$v_e=(2T_e/m_e)^{1/2}$ is the electron thermal velocity and $T_e$ is
electrons temperature.

@@

The dimensionless form of the particle kinetic equation has the
following form
\begin{equation}
  \begin{split}
    \frac{\partial \Phi_a({\bf u})}{\partial \tau}
    &= \frac{e_a^2}{e^2}\frac{m_e^2}{m_a^2}
    \sum_\sigma\sum_{\alpha=L,S}\int d{\bf q}\;\biggl(\frac{\bf q}{q}
    \cdot\frac{\partial}{\partial{\bf u}}\biggr)\,\mu_{\bf q}^\alpha
    \;\delta(\sigma z_{\bf q}^\alpha-{\bf q}\cdot{\bf u})\\
    & \times\,\biggl(g\frac{m_a}{m_e}\frac{\sigma z_{\bf q}^L}{q}
    \,\Phi_a({\bf u})+\calE_{\bf q}^{\sigma\alpha}
    \;\frac{\bf q}{q}\cdot\frac{\partial \Phi_a({\bf u})}
    {\partial{\bf u}}\biggr)+\sum_b\theta_{ab}(\Phi_a,\Phi_b),
    \label{Feu-evol}
  \end{split}
\end{equation}
where $\theta_{ab}(\Phi_a,\Phi_b)$ is the linearized Landau
collision integral, given by
\begin{equation}
  \begin{split}
     \theta_{ab}(\Phi_a,\Phi_b) &= \Gamma_{ab}\left\{
     \frac{\partial}{\partial{\bf u}_a}\cdot
     \left(2\frac{m_a}{m_b}\Psi(u_{ab})
     \frac{{\bf u}_a}{u^3_a}\Phi_a\right)\right.\\
  &+\frac{\partial}{\partial{\bf u}_a}\cdot
     \left\{\left[\left(\Phi(u_{ab})
     -\frac{1}{2 u_{ab}^2}\Psi(u_{ab})\right)
     \frac{\partial^2u_a}{\partial{\bf u}_a
     \partial{\bf u}_a}\right]\cdot
     \frac{\partial \Phi_a}{\partial{\bf u}_a}\right\}
    \label{eq:coll-lin} \\
  &+\left. \frac{\partial}{\partial{\bf u}_a}\cdot
     \left[\left(\frac{1}{u_{ab}^2}\Psi(u_{ab})
     \frac{{\bf u}_a{\bf u}_a}{u_a^3}\right)\cdot
   \frac{\partial \Phi_a}{\partial{\bf u}_a}\right]\right\},
\end{split}
\end{equation}
where $u_{ab}\equiv u_a (v_{T_a}/v_{T_b})$, $u_a=v_a/v_{T_a}$,
with $v_{T_a}$ and $v_{T_b}$ representing the thermal velocity of
the particles of species $a$ and $b$, respectively. The quantity
$\Psi(x)\equiv\Phi(x)-x\Phi'(x)$ is an auxiliary function \cite{
  Gaffey1976}, in which $\Phi(x) \equiv \frac{2}{\sqrt{\pi}}
\int_0^x e^{-t^2}dt$ is the error function and $\Phi'(x)=
\frac{2}{\sqrt{\pi}}e^{-x^2}$ is its derivative. The factor
$\Gamma_{ab}$ is given by $\Gamma_{ab}=2\pi g Z_b^2 \ln\Lambda $,
where $g=1/[2^{3/2}(4\pi)^2\hat n \lambda_{De}^3]$ is the plasma
parameter, $\ln \Lambda$ is Coulomb logarithm, and $Z_{b=e,i}$ is
the ion and electrons charge number, with $Z_e=1$.
The dispersion relations for $L$ and $S$ waves in dimensionless
form are given by
\begin{eqnarray*}
  z_{\bf q}^L = \left(1+\frac{3}{2}q^2\right)^{1/2},
 \quad   z_{\bf q}^S = \frac{q\, A}{(1+q^2/2)^{1/2}}, \quad
    A= \frac{1}{\sqrt{2}} \left(\frac{m_e}{m_i}\right)^{1/2}
     \left(1+3\frac{T_i}{T_e}\right)^{1/2}.
\end{eqnarray*}

@@

\chapter{Final remarks}
\label{cha:final}
In this text, we have summarized the early results of the analysis of a new first
principles theory, depicted in \Cref{noneigenmode}, which combines collective
processes (eigenmodes) and collisional interactions (noneigenmodes), for Langmuir
and ion-sound waves, without any \emph{ad hoc} addition. The importance of this
formalism, became clear right in the first study, presented in \Cref{coll-damp},
where it was shown the collisional damping rate calculated with the heuristic
Spitzer formula, that is independent of the wave-number, is highly overestimated
when compared with the rigorous expression, which has to be integrated in the
wave-number space. The Spitzer approximation is largely applied to the modeling
and interpretation of several solar phenomena observed by space-probes \cite{
  Vinas2000,Hannah2009,ZVST11,KRB12,KF13,Reid2014,Reid2015}, a fact that
emphasizes the necessity of the development of a mathematically rigorous
theory able to describe hybrid situations involving collective oscillations
and collisional interactions.

The second study, discussed in \Cref{sec:gen-supr}, was focused on the
consequences of taking into account the hitherto unknown effect of
electrostatic bremsstrahlung. The outcome of such analysis revealed an
underlying process, which takes the electron velocity distribution
out of its initial equilibrium state and transforms it into a new
quasi-equilibrium state that resembles a velocity distribution composed
by a Maxwellian core with a suprathermal tail. Such velocity distributions
are pervasively observed in space plasmas \cite{Parker1958a,Vasyliunas68,
  Coroniti1974,FABMG75,Lin1998,Horne2005,Clark2015,Padovani2015,deSoria2016,
  Padovani2017,Deca2017}. However, until these
days, despite several attempts of explanations based on different models,
no existing first principles approach is capable to self-consistently
describe its origin and evolution. Again, the relevance of this research
becomes evident. The ubiquity of inverse power-law velocity distribution
in space plasmas indicates the action of a fundamental physical process on
the plasma particles; this process may be the electrostatic bremsstrahlung.
For instance, the possibility of the formation of a suprathermal electron
distribution in a mildly collisional environment, as demonstrated in
\cite{Tigik2017a}, is in accordance with the velocity filtration model,
which rely on the existence of a high energy electron population in the
transition region, located between the chromosphere and the solar corona,
to explain the temperature inversion observed in the solar corona \cite{
  Scudder92a,Scudder92b,Anderson94,Scudder94,Scudder96,DS99,DS03,Teles15}.
Howsoever, the generality of the results of Ref. \cite{Tigik2017a} suggests
that collisional interactions involving charged particles enfold physical
processes that go beyond the Coulomb collisions effects, which might be
connected to some unexplained phenomena in plasma. Therefore, it is in
this context that the present doctoral working proposal is inserted.

% The prospects of this research are promising. Besides including the
% new effects on the time evolution of nonlinear beam-plasma interaction,
% we are planning the inclusion of effects due to non-homogeneous
% medium on the beam-plasma dynamics, and its implementation in the numerical
% code. Furthermore, the results regarding
% the electrostatic bremsstrahlung term deserve further research in order
% to confirm or discard the hypothesis made in Ref. \cite{Tigik2017a}, about
% the electrostatic bremsstrahlung being the underlying effect behind the
% generation of suprathermal velocity distributions, which are pervasively
% observed in space plasmas. The objectives above are in accordance with
% the research project approved for the ``Sandwich Doctorate Program'',
% that is proposed to occur under the supervision of Dr. Peter Yoon in the
% University of Maryland.

>>>>

Above, looking at the first noneigenmode term, in blue, one may notice
the extreme similarity with its previous expression, which describes the
spontaneous scattering process. In fact, this term is nothing but a
\emph{correction} to the spontaneous scattering process. Colored in
dark-green is the new, rigorous expression for the \emph{collisional
  damping}. The pink equation in the end, depicts the so-far unknown
\emph{electrostatic bremsstrahlung} process. The final expressions for
the three new contributions to the wave kinetic equation are given below.

@@

\chapter{Weakly turbulent processes in the presence of
  collisional interactions}
\label{main}
The generalization introduced in \cite{YZKS16} and summarized in
\Cref{noneigenmode}, is an innovative approach, in which the contribution
of the usually neglected noneigenmode fluctuations is taken into account
along with the well-known eigenmodes contribution. The outcome of this new
formulation is a first principles theory that combines both collective
and non-collective processes, assuming the propagation of electrostatic
oscillations in unmagnetized plasmas, without any \emph{ad hoc} addition.
Such theory is the basis of the present research, whose primary objective
is performing numerical analysis of the generalized weak turbulence equations,
and then investigate its applications on the description and interpretation
of space plasma phenomena. More specifically, the solar plasma, where the
results of the first two studies \cite{Tigik2016b,Tigik2017a} have shown a
promising perspective.

From the three new terms presented in the last chapter, we analyzed two:
the collisional damping \cite{Tigik2016b} and electrostatic bremsstrahlung
\cite{Tigik2017a}. The third term is a correction for the spontaneous
scattering effect, which is a nonlinear process. The first study, however,
analyses only the intensity of the collisional damping spectrum for $L$ and
$S$ waves by numerically integrating Eqs. \eqref{gammaL} and \eqref{gammaS},
respectively. Regarding the second study, the time evolution analysis was
made using quasilinear approximation, which does not involve nonlinear
wave-particle interaction, like the scattering effect. Besides that, a
small correction to a nonlinear term does not seem to justify a whole study
dedicated only to it.

In this chapter, we discuss some essential aspects regarding the results
obtained in both studies mentioned above. The results are presented in the
form of appended papers, using chronological order, in \Cref{coll-damp,sec:gen-supr}.

@@

The following paper is fairly self-sustained regarding the theory and
methods applied. All important equations are there, including their
normalized form and the normalization constants. 
% Any doubt regarding the origin of the new equations is filled by \Cref{noneigenmode}.

@@

\subsection{Dimensionless equations}
In order to simplify the numerical analysis, it is convenient to write
the equations in terms of dimensionless variables. Thus, let us start
by some important definitions
\begin{align*}
  z\equiv \frac{\omega}{\omega_{pe}},
  & \quad \tau\equiv \omega_{pe}t, \quad
    {\bf q}\equiv \frac{{\bf k}v_e}{\omega_{pe}}, \quad
    {\bf u}\equiv \frac{\bf v}{v_e},\\
  \mu_{\bf q}^L
  = 1,&\quad\mu_{\bf q}^S = \frac{q^3}{2^{3/2}}
	\,\sqrt{\frac{m_e}{m_i}}\;\biggl(1+\frac{3T_i}{T_e}\biggr)^{1/2},
\end{align*}
\begin{align*}
  \Phi_a({\bf u})=  v_e^3 F_a({\bf u}),& \quad
    \calE_{\bf q}^{\sigma\alpha}= \frac{(2\pi)^2 g}{m_ev_e^2}
    \frac{I_{\bf k}^{\sigma\alpha}}{\mu_{\bf k}^\alpha},\quad
    P_{\bf k}^\alpha=\frac{m_ev_e^2}{(2\pi)^2g}\omega_{pe}P_{\bf q}^\alpha,\\
\end{align*}
where $g=1/[2^{3/2}\,(4\pi)^2\,\hat{n}\,\lambda_{De}^3]$ is the
plasma parameter, $\lambda_{De}=T_e/(4\pi\hat{n}e^2)=v_e^2/(2\omega_{pe}^2)$,
$v_e=(2T_e/m_e)^{1/2}$ is the electron thermal velocity and $T_e$ is the
electron temperature.

@@

The dimensionless form of the particle kinetic equation has the
following form
\begin{equation}
  \begin{split}
    \frac{\partial \Phi_a({\bf u})}{\partial \tau}
    &= \frac{e_a^2}{e^2}\frac{m_e^2}{m_a^2}
    \sum_\sigma\sum_{\alpha=L,S}\int d{\bf q}\;\biggl(\frac{\bf q}{q}
    \cdot\frac{\partial}{\partial{\bf u}}\biggr)\,\mu_{\bf q}^\alpha
    \;\delta(\sigma z_{\bf q}^\alpha-{\bf q}\cdot{\bf u})\\
    & \times\,\biggl(g\frac{m_a}{m_e}\frac{\sigma z_{\bf q}^L}{q}
    \,\Phi_a({\bf u})+\calE_{\bf q}^{\sigma\alpha}
    \;\frac{\bf q}{q}\cdot\frac{\partial \Phi_a({\bf u})}
    {\partial{\bf u}}\biggr)+\sum_b\theta_{ab}(\Phi_a,\Phi_b),
    \label{Feu-evol}
  \end{split}
\end{equation}
where $\theta_{ab}(\Phi_a,\Phi_b)$ is the linearized Landau
collision integral, given by
\begin{equation}
  \begin{split}
     \theta_{ab}(\Phi_a,\Phi_b) &= \Gamma_{ab}\left\{
     \frac{\partial}{\partial{\bf u}_a}\cdot
     \left(2\frac{m_a}{m_b}\Psi(u_{ab})
     \frac{{\bf u}_a}{u^3_a}\Phi_a\right)\right.\\
  &+\frac{\partial}{\partial{\bf u}_a}\cdot
     \left\{\left[\left(\Phi(u_{ab})
     -\frac{1}{2 u_{ab}^2}\Psi(u_{ab})\right)
     \frac{\partial^2u_a}{\partial{\bf u}_a
     \partial{\bf u}_a}\right]\cdot
     \frac{\partial \Phi_a}{\partial{\bf u}_a}\right\}
    \label{eq:coll-lin} \\
  &+\left. \frac{\partial}{\partial{\bf u}_a}\cdot
     \left[\left(\frac{1}{u_{ab}^2}\Psi(u_{ab})
     \frac{{\bf u}_a{\bf u}_a}{u_a^3}\right)\cdot
   \frac{\partial \Phi_a}{\partial{\bf u}_a}\right]\right\},
\end{split}
\end{equation}
where $u_{ab}\equiv u_a (v_{T_a}/v_{T_b})$, $u_a=v_a/v_{T_a}$,
with $v_{T_a}$ and $v_{T_b}$ representing the thermal velocity of
the particles of species $a$ and $b$, respectively. The quantity
$\Psi(x)\equiv\Phi(x)-x\Phi'(x)$ is an auxiliary function \cite{
  Gaffey1976}, in which $\Phi(x) \equiv \frac{2}{\sqrt{\pi}}
\int_0^x e^{-t^2}dt$ is the error function and $\Phi'(x)=
\frac{2}{\sqrt{\pi}}e^{-x^2}$ is its derivative. The factor
$\Gamma_{ab}$ is given by $\Gamma_{ab}=2\pi g Z_b^2 \ln\Lambda $,
where $g=1/[2^{3/2}(4\pi)^2\hat n \lambda_{De}^3]$ is the plasma
parameter, $\ln \Lambda$ is Coulomb logarithm, and $Z_{b=e,i}$ is
the charge number of ions and electrons, with $Z_e=1$.
The dispersion relations for $L$ and $S$ waves in dimensionless
form are given by
\begin{eqnarray*}
  z_{\bf q}^L = \left(1+\frac{3}{2}q^2\right)^{1/2},
 \quad   z_{\bf q}^S = \frac{q\, A}{(1+q^2/2)^{1/2}}, \quad
    A= \frac{1}{\sqrt{2}} \left(\frac{m_e}{m_i}\right)^{1/2}
     \left(1+3\frac{T_i}{T_e}\right)^{1/2}.
\end{eqnarray*}

@@

\chapter{Final remarks}
\label{cha:final}
In this thesis, we have presented the results of the first analysis of a new
theory, depicted in \Cref{noneigenmode}, which combines collective processes
(eigenmodes) and collisional interactions (noneigenmodes), for Langmuir and
ion-sound waves, without any \emph{ad hoc} addition. The importance of this
formalism, became clear right in the first study, presented in \Cref{coll-damp},
where it was shown that the collisional damping rate calculated with the heuristic
Spitzer formula, that is independent of the wave-number, is highly overestimated
when compared with the rigorous expression, which has to be integrated in the
wave-number space. The Spitzer approximation is largely applied to the modeling
and interpretation of several solar phenomena observed by space-probes \cite{
  Vinas2000,Hannah2009,ZVST11,KRB12,KF13,Reid2014,Reid2015}, a fact that
emphasizes the necessity of the development of a mathematically rigorous
theory able to describe hybrid situations involving collective oscillations
and collisional interactions.

The second study, discussed in \Cref{sec:gen-supr}, focused on the
consequences of including the hitherto unknown effect of electrostatic
bremsstrahlung, in the time evolution of a Maxwellian electron velocity
distribution, under the quasilinear regime. The unexpected outcome of this
analysis revealed an underlying process responsible for taking the electron
velocity distribution out of its initial equilibrium state, leading it to
a new quasi-equilibrium state that is satisfied by a velocity distribution
composed by a Maxwellian core with a suprathermal tail. Such velocity
distributions are pervasively observed in space plasmas \cite{Parker1958a,
  Vasyliunas68,Coroniti1974,FABMG75,Lin1998,Horne2005,Clark2015,Padovani2015,
  deSoria2016,Padovani2017,Deca2017}. However, until these days, despite
several attempts of explaining how they form and why space plasmas are
particularly prone to develop a suprathermal tail while retaining the
thermal core, no existing theory is capable of describing self-consistently
its origin and evolution. Again, the relevance of this research becomes
evident.

The ubiquity of inverse power-law velocity distribution in space plasmas
indicates the action of a fundamental physical process; this process may
be the electrostatic bremsstrahlung. For instance, the possibility of the
formation of suprathermal electron velocity distributions in a mildly
collisional environment, as demonstrated in \cite{Tigik2017a}, has a positive
correlation with the velocity filtration model, which rely on the existence
of a high energy electron population in the transition region, located between
the chromosphere and the solar corona, to explain the temperature inversion
observed in the solar corona \cite{Scudder92a,Scudder92b,Anderson94,Scudder94,
  Scudder96,DS99,DS03,Teles15}.

As a final remark, we would like to emphasize the fundamental aspect of the
theory presented in Ref. \cite{YZKS16}. The rigorous analysis performed during
this doctoral research, suggest that collisional interactions involving charged
particles enfold physical processes that go beyond the Coulomb collisions
effects. An enthralling prospect of this study lies in the possibility of these
underlying kinetic processes being connected to unexplained phenomena observed
in space plasmas. On that regard...

% It is time for new advances in the kinetic description of plasmas. For
% a long time, space observations could only resolve physical phenomena occurring
% in macroscopic scales, described by the magnetohydrodynamic (MHD) theory.

% A better understanding of the combined action of collective and collisional
% plasma processes has some important impact on how observational data from
% denser regions of the solar corona are analyzed. Now that the Parker solar
% probe 
% The prospects of this research are promising. Besides including the
% new effects on the time evolution of nonlinear beam-plasma interaction,
% we are planning the inclusion of effects due to non-homogeneous
% medium on the beam-plasma dynamics, and its implementation in the numerical
% code. Furthermore, the results regarding
% the electrostatic bremsstrahlung term deserve further research in order
% to confirm or discard the hypothesis made in Ref. \cite{Tigik2017a}, about
% the electrostatic bremsstrahlung being the underlying effect behind the
% generation of suprathermal velocity distributions, which are pervasively
% observed in space plasmas. The objectives above are in accordance with
% the research project approved for the ``Sandwich Doctorate Program'',
% that is proposed to occur under the supervision of Dr. Peter Yoon in the
% University of Maryland.
